### 2018-04-26 paper/algorithm.tex
SPOR: changes Secure to Stateless
Updates SPOR subsection title
Adds use of breqn package

\subsection{\(\SPOR\)}

@@

We have the Secure Probabilistic Onion Routing scheme, \SPOR, which provides 
probabilistically onion-routed message passing.
Instead of providing only one address per hop in the route (as in \eg 
Tor~\cite{Tor}), \(\SPOR\) provides several alternatives for the next hop 
depending on their probability of being online.
To do this, \(\SPOR\) provides stateless algorithms for the onion-routing.

@@

We select several relays at each point of the route: $R_i=\{r_{i,j}\}$ would be the \emph{set} of possibly disconnected devices that will take the $i^\text{th}$ position in our onion route.
In traditional onion routing, $r_1$ is the only one knowing the address of $r_2$, because it is written encrypted with its public key in the header.
Here, every device in the $R_i$ can read the set $R_{i+1}$ in the header, because the symmetric key $sk$ used to encrypt the set $R_{i+1}$ is known to every device in $R_i$.
The header indeed contains a version of $sk$ for each device $r_{i,j}$, encrypted with its own public key $pk_{r_{i,j}}$.

>>>>

\subsection{\(\SPOR\): Stateless Predictive Onion Routing}

@@

We have the Stateless Predictive Onion Routing scheme, \SPOR, which provides 
probabilistically onion-routed message passing.
Instead of providing only one address per hop in the route (as in \eg 
Tor~\cite{Tor}), \(\SPOR\) provides several alternatives for the next hop 
depending on their probability of being online.
To do this, \(\SPOR\) provides stateless algorithms for the onion-routing.

@@

We select several relays at each point of the route: $R_i=\{r_{i,j}\}$ would be 
the \emph{set} of possibly disconnected devices that will take the 
$i^{\text{th}}$ position in our onion route.
In traditional onion routing, $r_1$ is the only one knowing the address of $r_2$, because it is written encrypted with its public key in the header.
Here, every device in the $R_i$ can read the set $R_{i+1}$ in the header, because the symmetric key $sk$ used to encrypt the set $R_{i+1}$ is known to every device in $R_i$.
The header indeed contains a version of $sk$ for each device $r_{i,j}$, encrypted with its own public key $pk_{r_{i,j}}$.
